Notes for Week 5/29/19 - 5/31/19

### 2019-06-07 notes/weekly_notes/5.29.19.NotesForWeek.tex
weekly notes updated

%%% Vectors

@@

%%% Operators
\newcommand{\Tadj}{T^{\star}}
\newcommand{\dive}{\mathrm{div}}
\newcommand{\dif}{\mathop{}\!\mathrm{d}}

%%% Misc
\newcommand{\grid}{\mathrm{grid}}
\newcommand{\critr}{R_n}

@@

\begin{document}
\title{Notes for Week 5/15/19 - 5/17/19}
\author{Alden Green}
\date{\today}
\maketitle

@@

Define the \emph{Laplacian Smooth} test statistic over the neighborhood graph to be
\begin{equation*}
T_{LS} = \sup_{\theta: \norm{D_{r}\theta}_2 \leq C(n,r)} \dotp{\theta }{\frac{1_X}{N_X} - \frac{1_Y}{N_Y}}
\end{equation*}
where we note that the test statistic is implicitly a function of $r$ and $C(n,r)$.

\paragraph{General assumptions.}
We will need to make the following assumptions in order to obtain meaningful theoretical results.

\begin{assumption}[General assumptions.]
	\label{asmp: general}
	For each $f \in \mathcal{H}$, assume $\mathrm{supp}(f)$ is an open connected, bounded subset of $\Rd$ with $l$-Lipschitz boundary. Further assume $\mathcal{H}$ is uniformly bounded above and below: that is, there exists $f_{\min} < f_{\max}$ such that for each $f \in \mathcal{H}$, 
	\begin{equation*}
	0 < f_{\min} < f(x) < f_{\max} < \infty, \quad \textrm{for all $x \in \mathrm{supp}(f)$}
	\end{equation*}
\end{assumption}

We motivate these assumptions through the following theorem relating the $r$-neighborhood graph to the $d$-dimensional grid, a useful result as the spectrum of grid graphs is well known.

Formally, for $\kappa = n^{1/d}$, consider the \emph{grid graph}
\begin{equation*}
G_{grid} = (V_{grid},E_{grid}),~~ V_{grid} = \set{k: k \in [\kappa]^d},~~ E_{grid} = \set{(k,k'): k, k' \in V_{grid}, \norm{k - k'}_1 = 1}
\end{equation*}
with associated incidence matrix $D_{grid}$.

\begin{lemma}
	Let $z_1, \ldots,z_n \sim p$ for some density function $p \in \mathcal{H}$ which satisfies Assumption \ref{asmp: general}.

	Fix $a > 2$. There exists $c_1 > 0$ (potentially depending on $d, l, f_{\min}, f_{\max}$ and $a$) such that for any $r \geq c_1 \left(\frac{\log n}{n}\right)^{1/d}$, the following statement holds with probability at least $1 - n^{-a}$: there exists a bijection $T: [n] \to [\kappa]^d$ such that for all $\theta = (\theta_1, \ldots, \theta_n) \in \Reals^n$, letting
	\begin{equation*}
	(\theta_{T})_{k} = \theta_{T^{-1}(k)}, \textrm{for all $k \in [\kappa]^d$}
	\end{equation*}
	we have
	\begin{equation*}
	\norm{D_{\grid}\theta_{T}}_2 \leq \norm{D_r \theta}_2.
	\end{equation*}
\end{lemma}
\textcolor{red}{Prove this.}

We use this to control the empirical process $T_{LS}$ under the null hypothesis.
\begin{lemma}
	Assume $\mathcal{H}$ satisfies Assumption \ref{asmp: general}, and fix $a \geq 2$. Then, there exists $c_1 > 0$ (potentially depending on $d, l, f_{\min}$, $f_{\max}$, and $a$) and $c_2$ (potentially depending on $d$) such that for any $r \geq c_1 \left(\frac{\log n}{n}\right)^{1/d}$, and any $C_{n,r} > 0$,
	\begin{equation*}
	\Pbb_{\mathbb{H}_0}\left(T_{LS} \leq \frac{c_2 C(n,r)\sqrt{\log n} }{a \sqrt{n}} \right) \leq 1 - 2\exp(2a) - a
	\end{equation*}
\end{lemma}
\begin{proof}
	We write
	\begin{align*}
	T_{LS} & \leq \abs{T_{LS} - \sup_{\substack{\theta: \norm{D_r \theta}_2 \leq C(n,r), \\ \theta^T \mathbf{1} = 0} } \frac{1}{n/2}\dotp{\theta}{1_X - 1_Y}} + \sup_{\substack{\theta: \norm{D_r \theta}_2 \leq C(n,r), \\ \theta^T \mathbf{1} = 0} } \frac{1}{n/2}\dotp{\theta}{1_X - 1_Y} \\
	& \leq \abs{T_{LS} - \sup_{\substack{\theta: \norm{D_r \theta}_2 \leq C(n,r), \\ \theta^T \mathbf{1} = 0} } \frac{1}{n/2}\dotp{\theta}{1_X - 1_Y}} + \sup_{\substack{\theta: \norm{D_{\grid} \theta}_2 \leq C(n,r), \\ \theta^T \mathbf{1} = 0} } \frac{1}{n/2}\dotp{\theta}{1_X - 1_Y} \tag{Lemma \ref{lem: closed_form_ls_statistic} } \\
	& \leq \abs{T_{LS} - \sup_{\substack{\theta: \norm{D_r \theta}_2 \leq C(n,r), \\ \theta^T \mathbf{1} = 0} } \frac{1}{n/2}\dotp{\theta}{1_X - 1_Y}} + C(n,r) \frac{1}{n/2} \sqrt{\sigma^T L_{\grid}^{\dagger} \sigma}
	\end{align*}
	whence the statement follows by Lemmas \ref{lem: normalization_error} and \ref{lem: noise_quadratic_form_on_grid}.
\end{proof}

\section{Additional Theory}

The Laplacian smooth test statistic has a closed form solution. Let $L = D^T D$ be the Laplacian of $G$, and write $\Linv$ for the pseudoinverse of $L$.

\begin{lemma}
	\label{lem: closed_form_ls_statistic}
	For any unweighted, undirected, connected graph $G = (V,E)$ with incidence matrix $D$, number $C > 0$, and any vector $v \in \Reals^n$ with $\sum_{i = 1}^{n} v_i = 0$,
	\begin{equation*}
	\sup_{\theta: \norm{D\theta}_2 \leq C} \dotp{\theta}{v} = C \sqrt{v^T \Linv v}
	\end{equation*}
	Additionally, for any vector $v \in \Reals^n$ (not necessarily $\sum_{i = 1}^{n} v_i = 0$), under the additional constraint $\theta^T \mathbf{1} = 0$, the same statement holds. That is,
	\begin{equation*}
	\sup_{ \substack{\theta: \norm{D\theta}_2 \leq C, \\ \theta^T \mathbf{1} = 0} } \dotp{\theta}{v} = C \sqrt{v^T \Linv v}
	\end{equation*}
\end{lemma}
\begin{proof}
	Note that the condition $\norm{D \theta}_2 \leq C$ is equivalent to $\theta^T L \theta \leq C$. The solution then follows from the KKT conditions.
\end{proof}

\begin{lemma}
	\label{lem: normalization_error}
	Under the general assumptions,
	\begin{equation*}
	\abs{T_{LS} - \sup_{\substack{\theta: \norm{D_r \theta}_2 \leq C(n,r), \\ \theta^T \mathbf{1} = 0} } \frac{1}{n/2}\dotp{\theta}{1_X - 1_Y}} \leq \frac{8C(n,r)}{a n^{1 - 1/d}\pi}
	\end{equation*}
	with probability at least $1 - 2 \exp(2a)$. 
\end{lemma}
\begin{proof}
	Note that as $(1_X/N_X - 1_Y/X_Y)^T \mathbf{1} = 0$, we may write
	\begin{align*}
	T_{LS} & = \sup_{\substack{\theta: \norm{D_r \theta}_2 \leq 1, \\ \theta^T \mathbf{1} = 0} } \dotp{\theta}{\frac{1_X}{N_X} - \frac{1_Y}{N_Y}}
	\end{align*}
	and therefore by Cauchy-Schwarz,
	\begin{align*}
	\abs{T_{LS} - \sup_{\substack{\theta: \norm{D_r \theta}_2 \leq C, \\ \theta^T \mathbf{1} = 0} } \frac{1}{n/2}\dotp{\theta}{1_X - 1_Y}}  & \leq \sup_{\substack{\theta: \norm{D_r \theta}_2 \leq C, \\ \theta^T \mathbf{1} = 0} } \set{\norm{\theta}} \cdot \norm{1_X(2/n - 1/N_X) - 1_Y(1/N_Y - 2/n)} \\
	& \leq \sup_{\substack{\theta: \norm{D_r \theta}_2 \leq C, \\ \theta^T \mathbf{1} = 0} } \set{\norm{\theta}} \cdot \norm{1_X(2/n - 1/N_X) - 1_Y(1/N_Y - 2/n)} \\
	& \leq \sup_{\substack{\theta: \norm{D_r \theta}_2 \leq C, \\ \theta^T \mathbf{1} = 0} } \set{\norm{\theta}} \cdot \left(\norm{1_X} \frac{\abs{n/2 - N_X}}{n/2 N_X} + \norm{1_Y} \frac{\abs{n/2 - N_Y}}{n/2 N_Y}\right) \\
	& \leq \sup_{\substack{\theta: \norm{D_r \theta}_2 \leq C, \\ \theta^T \mathbf{1} = 0} } \set{\norm{\theta}} \cdot \left(\frac{2\abs{n/2 - N_X}}{\sqrt{N_X} n} + \frac{2\abs{n/2 - N_Y}}{\sqrt{N_Y} n} \right).
	\end{align*}
	The reasoning in the proof of Lemma \ref{lem: noise_quadratic_form_on_grid} leads to the bound
	\begin{equation*}
	\sup_{\substack{\theta: \norm{D_r \theta}_2 \leq C, \\ \theta^T \mathbf{1} = 0} } \set{\norm{\theta}} \leq \frac{C n^{1/d}}{\pi},
	\end{equation*}
	and a standard application of Hoeffding's inequality to the quantities $N_X$ and $N_Y$ yields, for any $a > 0$
	\begin{equation*}
	\abs{N_X - n/2}, \abs{N_Y - n/2} \leq  a \sqrt{n}
	\end{equation*}
	with probability at least $1 - 2 \exp(-2a)$. As a result,
	\begin{equation*}
	\sup_{\substack{\theta: \norm{D_r \theta}_2 \leq 1, \\ \theta^T \mathbf{1} = 0} } \set{\norm{\theta}} \cdot \left(\frac{2\abs{n/2 - N_X}}{\sqrt{N_X} n} + \frac{2\abs{n/2 - N_Y}}{\sqrt{N_Y} n} \right) \leq \frac{8a C n^{1/d}}{n\pi} 
	\end{equation*}
	with probability at least $1 - 2 \exp(-2a)$, which proves the claim.
\end{proof}

\subsection{Type I error.}

Denote the eigenvalues and eigenvectors of $\Lgrid = \Dgrid^T \Dgrid$ as $\set{\lambda_{k}: k \in [\kappa]^d}$ and $\set{u_{k}: k \in [\kappa]^d}$, respectively.

\begin{lemma}
	\label{lem: noise_quadratic_form_on_grid}
	Let $\sigma_1, \ldots, \sigma_n \sim \mathrm{Rademacher}(1/2)$ be independent random variables, and write $\sigma = (\sigma_1, \ldots, \sigma_n)$. Then, 
	\begin{equation*}
	\sigma^T \Linvgrid \sigma \leq \frac{(2d)^d\kappa^2}{a\pi^2} \left(8 + 2\pi \log(\sqrt{2} \kappa) \left(\sum_{p = 2}^{d}\kappa^{p}\right) \right)
	\end{equation*}
	with probability at least $1  - a$.
\end{lemma}
\begin{proof}
	Taking the eigendecomposition $\Lgrid = U \Lambda U^T$, we can then write $\Linvgrid = U \Lambda^{\dagger} U^T$. Therefore
	\begin{equation*}
	\Ebb \bigl(\sigma^T \Linvgrid \sigma\bigr) = \sum_{k \in [\kappa]^d} \frac{\Ebb \bigl(u_{k}^T \sigma\bigr)^2}{\lambda_k}
	\end{equation*}
	and as 
	\begin{equation*}
	\Ebb \bigl(u_{k}^T \sigma\bigr)^2 = \sum_{i,j = 1}^{n} \Ebb(u_{k_i} u_{k_j} \sigma_i \sigma_j) = \sum_{i = 1}^{n} u_{k_i}^2 = 1
	\end{equation*}
	we are left with
	\begin{equation}
	\label{eqn: noise_quadratic_form_on_grid_1}
	\Ebb \bigl(\sigma^T \Linvgrid \sigma\bigr) = \sum_{\substack{k \in [\kappa]^d, \\ k \neq \bf{0}}} \frac{1}{\lambda_k}.
	\end{equation}

	It is well known \textcolor{red}{HR, CB}, that the $d$-dimensional grid can be written as the Kronecker product of $d$ path graphs, and exploiting this fact as in \textcolor{red}{SWT} we obtain
	\begin{align*}
	\lambda_{k} = 4 \sin^2\left(\frac{\pi(k_1 - 1)}{2 \kappa}\right) + \cdots + 4 \sin^2\left(\frac{\pi(k_d - 1)}{2 \kappa}\right).
	\end{align*}
	The inequality $\sin(x) \geq x/2$ holds for $x \in [0,\pi/2]$, and so we have
	\begin{align*}
	\sum_{\substack{k \in [\kappa]^d, \\ k \neq \bf{0}}} \frac{1}{\lambda_k} & \leq \frac{\kappa^2}{\pi^2} \sum_{\substack{k \in [\kappa]^d, \\ k \neq \bf{0}}} \left(\sum_{j = 1}^{d} (k_j - 1)^2\right)^{-1} \\
	& \leq \frac{(2d)^d\kappa^2}{\pi^2} \left(8 + 2\pi \log(\sqrt{2} \kappa) \left(\sum_{p = 2}^{d}\kappa^{p - 2}\right) \right) \\
	& = \frac{(2d)^d\kappa^2}{\pi^2} \left(8 + 2\pi \log(\sqrt{2} \kappa) \left(\sum_{p = 2}^{d}\kappa^{p}\right) \right) \tag{Lemma \ref{lem: grid_eigenvalues}}
	\end{align*}
	whence the claim follows by Markov's inequality.
\end{proof}

\begin{lemma}
	\label{lem: grid_eigenvalues}
	There exists a universal constant $c_1 > 0$ such that for any $\kappa \geq 1$ and for all integers $d \geq 3$,
	\begin{equation*}
	\sum_{\substack{k \in [\kappa]^d, \\ k \neq \bf{0}}} \left(\sum_{j = 1}^{d} (k_j - 1)^2\right)^{-1} \leq (2d)^d \Biggl(8 + 2 \pi \log (\sqrt{2} \kappa) \biggl(\sum_{p = 2}^{d} \kappa^{p - 2}\biggr) \Biggr)
	\end{equation*}
\end{lemma}
\begin{proof}
	We will prove by induction on $d$. As a base case, consider $d  = 2$. Rewrite
	\begin{equation*}
	\sum_{\substack{k \in [\kappa]^d, \\ k \neq \bf{0}}} \left(\sum_{j = 1}^{d} (k_j - 1)^2\right)^{-1} \leq 4 \sum_{k_1 = 1}^{\kappa - 1} \frac{1}{k_1^2}  + \sum_{k_1 =2}^{\kappa - 1} \sum_{k_2 = 2}^{\kappa - 1} (k_1^2 + k_2^2)^{-1}.
	\end{equation*}
	Then, upper bounding sums by integrals, we obtain
	\begin{equation*}
	\sum_{k_1 = 1}^{\kappa - 1} \frac{1}{k_1^2} \leq 1 +  \int_{x = 1}^{\kappa} \frac{1}{x^2} \dif x \leq 2,
	\end{equation*}
	and 
	\begin{align*}
	\sum_{k_1 = 2}^{\kappa - 1} \sum_{k_2 = 2}^{\kappa - 1} (k_1^2 + k_2^2)^{-1} & \leq \int_{x = 1}^{\kappa} \int_{y = 1}^{\kappa} \frac{1}{x^2 + y^2} \dif x \dif y \\
	& \leq 2 \pi \log(\sqrt{2} \kappa),
	\end{align*}
	so that
	\begin{equation*}
	\sum_{\substack{k \in [\kappa]^d, \\ k \neq \bf{0}}} \left(\sum_{j = 1}^{d} (k_j - 1)^2\right)^{-1} \leq 8 + 2 \pi \log(\sqrt{2} \kappa).
	\end{equation*}
	and the base case is shown.

	We proceed by induction. For $d \geq 3$ we write
	\begin{align*}
	\sum_{\substack{k \in [\kappa]^d, \\ k \neq \bf{0}}} \left(\sum_{j = 1}^{d} (k_j - 1)^2\right)^{-1} & \leq 2d \sum_{\substack{k \in [\kappa]^{d - 1}, \\ k \neq \bf{0}}} \left(\sum_{j = 1}^{d - 1} (k_j - 1)^2\right)^{-1} + \sum_{k_1 = 2}^{\kappa - 1} \cdots \sum_{k_d = 2}^{\kappa - 1} \left(\sum_{j = 1}^{d} k_j^2\right)^{-1} \\
	& \leq 2d \left( (2d)^{d - 1}\Biggl(8 + 2 \pi \log \sqrt{2} \kappa \biggl(\sum_{p = 2}^{d - 1} \kappa^{p - 2}\biggr) \Biggr)\right) + \sum_{k_1 = 2}^{\kappa - 1} \cdots \sum_{k_d = 2}^{\kappa - 1} \left(\sum_{j = 1}^{d} k_j^2\right)^{-1} \\
	& = \left( (2d)^{d}\Biggl(8 + 2 \pi \log \sqrt{2} \kappa \biggl(\sum_{p = 2}^{d - 1} \kappa^{p - 2}\biggr) \Biggr)\right) + \sum_{k_1 = 2}^{\kappa - 1} \cdots \sum_{k_d = 2}^{\kappa - 1} \left(\sum_{j = 1}^{d} k_j^2\right)^{-1} 
	\end{align*}
	and again upper bounding sums by integrals, we obtain
	\begin{align*}
	\sum_{k_1 = 2}^{\kappa - 1} \cdots \sum_{k_d = 2}^{\kappa - 1} \left(\sum_{j = 1}^{d} (k_j)^2\right)^{-1} & \leq \int_{1}^{\kappa} \cdots \int_{1}^{\kappa} \frac{1}{x_1^2 + \cdots + x_d^2} \dif x_d \ldots \dif x_1 \\
	& \leq \kappa^{d-2} \int_{1}^{\kappa} \int_{1}^{\kappa} \frac{1}{x^2 + y^2} \dif x \dif y \\
	& \leq \kappa^{d-2} 2 \pi \log(\sqrt{2} \kappa)
	\end{align*}
	and the proof is complete.
\end{proof}

\paragraph{Type II error.}

Lemma \ref{lem: approx_error_lb_1} will be useful in lower bounding the \textcolor{red}{approximation error} of the $T_{LS}$ test statistic. Write $P_1^{\perp}$ for the projection operator onto the subspace of $\Reals^n$ orthogonal to the constant vector $\mathbf{1}$.

\begin{lemma}
	\label{lem: approx_error_lb_1}
	For any vector $v \in \Reals^n$ and Laplacian matrix $L$ of a connected graph $G$,
	\begin{equation*}
	v^T \Linv v \geq \frac{(v^T P_{1}^{\perp}v)^2}{v^T L v}
	\end{equation*}
\end{lemma}
\begin{proof}
	We can expand $v^T P_1^{\perp} v  = v^T (L)^{1/2}(\Linv)^{1/2} v$, for any matrix square root of $L$ and $\Linv$. The statement follows by Cauchy-Schwarz.
\end{proof}

>>>>

%%% Vectors
\newcommand{\thetast}{\theta^{\star}}

@@

%%% Operators
\newcommand{\Tadj}{T^{\star}}
\newcommand{\dive}{\mathrm{div}}
\newcommand{\dif}{\mathop{}\!\mathrm{d}}
\newcommand{\gradient}{\mathcal{D}}
\newcommand{\Hessian}{\mathcal{D}^2}

%%% Misc
\newcommand{\grid}{\mathrm{grid}}
\newcommand{\critr}{R_n}
\newcommand{\dx}{\,dx}
\newcommand{\dy}{\,dy}

@@

\begin{document}
\title{Notes for Week 5/29/19 - 5/31/19}
\author{Alden Green}
\date{\today}
\maketitle

@@

Define the \emph{Laplacian Smooth} test statistic over the neighborhood graph to be
\begin{equation*}
T_{LS} = \sup_{\theta: \norm{D\theta}_2 \leq C(n,r)} \dotp{\theta }{\frac{1_X}{N_X} - \frac{1_Y}{N_Y}}
\end{equation*}
where we note that the test statistic is implicitly a function of $r$ and $C(n,r)$.

\section{Additional Theory}
Let $\theta^{\star} = (\thetast_i)_{i = 1}^n$, with $\thetast_i := f(z_i) - g(z_i)$. Write $L = D^T D$ for the Laplacian matrix of the $r$-neighborhood graph, $\gradient f$ for the gradient of a function $f$, and $\Hessian f$ for the Hessian of a function $f$. We write $C^{2}(L)$ for the set of functions $f$ twice continuously differentiable over $\Rd$, with bounded Hessian $\norm{\Hessian f}_{\infty} \leq L$.
\begin{lemma}
	\label{lem: approx_error}
	For all density functions $f,g \in C^2(L)$ with $\int (f - g)^2 \geq \epsilon^2$, if $r \geq c_1 (\log n / n)^{1/d}$ and $\epsilon \geq c_2 n r^{d + 1} $ then
	\begin{equation*}
	\sup_{\norm{D\theta}_2 \leq 1} \dotp{\theta}{\thetast} \geq \frac{c_2}{2} (\log n)^{1 + 2/d} n^{-2/d}
	\end{equation*}
	with probability at least $1 - \delta$.
\end{lemma}
\begin{proof}
	By Lemmas \ref{lem: closed_form_ls_statistic} and \ref{lem: lin_alg_1}, we have
	\begin{align}
	\label{eqn: approx_error_1}
	\sup_{\norm{D\theta}_2 \leq 1} \dotp{\theta}{\thetast} & = \frac{1}{n} \sqrt{(\thetast)^T \Linv \thetast} \nonumber \\
	& \geq \frac{1}{\lambda_k}\left(\dotp{\thetast}{\thetast} - \dotp{P_k^{\perp} \thetast}{P_k^{\perp}\thetast}\right)^2 
	\end{align}
	where the latter inequality holds for any $k = 1, \ldots, n - 1$. We upper bound $\dotp{P_k^{\perp} \thetast}{P_k^{\perp}\thetast}$ using the following relations
	\begin{equation*}
	(\thetast)^T L \thetast \geq (P_k^{\perp}\thetast)^T \Linv ( P_k^{\perp}\thetast) \geq \lambda_k \dotp{P_k^{\perp} \thetast}{P_k^{\perp} \thetast}
	\end{equation*}
	and obtain
	\begin{align*}
	\frac{1}{\lambda_k}\left(\dotp{\thetast}{\thetast} - \dotp{P_k^{\perp} \thetast}{P_k^{\perp}\thetast}\right)^2  & \geq \frac{1}{\lambda_k}\left(\dotp{\thetast}{\thetast} - \frac{(\thetast)^T L \thetast}{\lambda_k} \right)^2 \\
	& \geq \frac{1}{\lambda_k}\left(c_1 n \epsilon^2 - \frac{c_2 n^2 r^{d + 2}}{\lambda_k} \right)^2 \tag{Lemmas \ref{lem: witness_inner_product} and \ref{lem: witness_discrete_energy}}
	\end{align*}
	where the latter inequality occurs with probability at least $1 - 2\delta$. Choose $k = n - 1$. As $r \geq c_1 (\log n / n)^{1/d}$, we have that $G \preceq \mathrm{Grid}$, and as a result \textcolor{red}{$4 \geq \lambda_{n - 1} \geq 1$}. Therefore,
	\begin{align*}
	\frac{1}{\lambda_k}\left(c_1 n \epsilon^2 - \frac{c_2 n^2 r^{d + 2}}{\lambda_k} \right)^2 & \geq \frac{1}{4} \left(c_1 n \epsilon^2 - c_2 n^2 r^{d + 2} \right)^2 \\
	& \geq \frac{1}{4} \left(c_2 n^2 r^{d + 2}\right)^2 \\
	& \geq \frac{1}{4} \left(c_2 n^{1 - 2/d} \log(n)^{1 + 2/d}\right)^2 = \frac{c_2^2}{4} n^{2 - 4/d} \log(n)^{2 + 4/d},
	\end{align*}
	and the proof is complete.
\end{proof}

\begin{lemma}
	\label{lem: witness_inner_product}
	For any $f, g \in L^2(\Rd)$ satisfying the \textcolor{red}{regularity conditions}, such that $\int_{\Rd} (f - g)^2 dx \geq \epsilon^2$ there exists constant $c_1$ such that 
	\begin{equation*}
	\dotp{\thetast}{\thetast} \geq c_1 n \epsilon^2
	\end{equation*}
	with probability at least $1 - \delta$.
\end{lemma}

\begin{lemma}
	\label{lem: witness_discrete_energy}
	For any $f, g \in C^2(L)$ satisfying the \textcolor{red}{regularity conditions}, there exists a constant $c_2$ such that
	\begin{equation*}
	(\thetast)^T L \thetast \leq c_2 n^2 r^{d + 2}
	\end{equation*}
	with probability at least $1 - \delta$.
\end{lemma}

\section{Linear Algebra}

\begin{lemma}
	\label{lem: closed_form_ls_statistic}
	For any unweighted, undirected, connected graph $G = (V,E)$ with incidence matrix $D$, and any vector $v \in \Reals^n$ with $\sum_{i = 1}^{n} v_i = 0$,
	\begin{equation*}
	\sup_{\theta: \norm{D\theta}_2 \leq C} \dotp{\theta}{v} = C \sqrt{v^T \Linv v}
	\end{equation*}
	Additionally, for any vector $v \in \Reals^n$ (not necessarily $\sum_{i = 1}^{n} v_i = 0$), under the additional constraint $\theta^T \mathbf{1} = 0$, the same statement holds. That is,
	\begin{equation*}
	\sup_{ \substack{\theta: \norm{D\theta}_2 \leq C, \\ \theta^T \mathbf{1} = 0} } \dotp{\theta}{v} = C \sqrt{v^T \Linv v}
	\end{equation*}
\end{lemma}
\begin{proof}
	Note that the condition $\norm{D \theta}_2 \leq C$ is equivalent to $\theta^T L \theta \leq C$. The solution then follows from the KKT conditions.
\end{proof}

Let $L$ be the Laplacian matrix of a connected graph, and $\Linv$ be the pseudo-inverse $L$. Write the eigendecomposition of $\Linv = U\Lambda^{\dagger}U^{T}$, where $\Lambda$ is an $n \times n$ diagonal matrix with entries $0 = \lambda_0 < \lambda_1 \leq \lambda_2 \leq \ldots \leq \lambda_{n-1}$ and $U$ is an orthogonal matrix with columns $U =\left(u_0 \ldots u_{n-1}\right)$. For each $k = 0, \ldots, n - 1$, write $U_{k} = (u_0 \ldots u_{k-1})$ for the first $k$ columns of $U$, $P_k$ as the projection operator onto the span of $U_k$, and $P_k^{\perp}$ for the projection operator onto the subspace orthogonal to the span of $U_k$.
\begin{lemma}
	\label{lem: lin_alg_1}
	For any $k = 1, \ldots, n$, 
	\begin{equation*}
	(\thetast)^T \Linv \thetast \geq \frac{1}{\lambda_k}\left(\dotp{\thetast}{\thetast} - \dotp{P_k^{\perp} \thetast}{P_k^{\perp}\thetast}\right)^2
	\end{equation*}
\end{lemma}
\begin{proof}
	Note that $\Lambda^{\dagger}$ is a diagonal matrix, with entries $\rho_{1,1} = 0$ and $\rho_{k,k} = \frac{1}{\lambda_k}$ for $k = 1, \ldots, n$. Therefore,
	\begin{equation*}
	(\thetast)^T \Linv \thetast = \sum_{k = 1}^{n} \frac{\dotp{\thetast}{u_k}^2}{\lambda_k}.
	\end{equation*}
	Clearly, for any $k = 1, \ldots, n$,
	\begin{equation*}
	\sum_{k = 1}^{n} \frac{\dotp{\thetast}{u_k}^2}{\lambda_k} \geq \frac{\dotp{P_k \thetast}{P_k \thetast}^2}{\lambda_k}
	\end{equation*}
	and as $\dotp{P_k \thetast}{P_k \thetast} + \dotp{P_k^{\perp} \thetast}{P_k^{\perp} \thetast} = \dotp{\thetast}{\thetast}$, we obtain
	\begin{align*}
	\frac{\dotp{P_k \thetast}{P_k \thetast}^2}{\lambda_k} & =  \frac{1}{\lambda_k}\left(\dotp{\thetast}{\thetast} - \dotp{P_k^{\perp} \thetast}{P_k^{\perp}\thetast}\right)^2.
	\end{align*}
\end{proof}
